Generalised gravitational burst searches with Generative Adverserial Networks~\chris{Need to change the title if we don't search}

### 2020-02-26 Paper_draft/GAN_paper.tex
Update GAN_paper.tex

\begin{abstract}
As the field of gravitational wave astronomy expands and as detectors become
more sensitive, there is a need for fast and efficient detection of various
sources. Gravitational wave bursts are a family of signals that remain
unmodeled, therefore, they have a low detection sensitivity to standard
detection schemes. This report examines the use of Generative Adversarial
Networks as a detection pipeline for gravitational wave burst signals. BurstGAN
is trained to detect three classes of burst signals: sine-Gaussian, Ring-downs
and white-noise bursts contained in white Gaussian noise. The resulting
sensitivity curves show that sine-Gaussian and Ring-downs are confidently
detectable at SNRs > while white-noise bursts require SNRs of >.~\chris{we'll
fix the abstract at the end}
%\begin{description} \item[Usage] Secondary publications and information
%retrieval purposes.  \item[Structure] You may use the \texttt{description}
%environment to structure your abstract; use the optional argument of the
%\verb+\item+ command to give the category of each item.  \end{description}
\end{abstract}

>>>>

\begin{abstract}
f >.~\chris{we'll
fix the abstract at the end}
%\begin{description} \item[Usage] Secondary publications and information
%retrieval purposes.  \item[Structure] You may use the \texttt{description}
%environment to structure your abstract; use the optional argument of the
%\verb+\item+ command to give the category of each item.  \end{description}
\end{abstract}
